### 2018-01-17 CO681-QuantumInformationProcessing/project/network-flows.tex
Wrote up problem 1

In the list model, each vertex is processed in time $$O(\sqrt{\frac{n_v}{d(v)}}d_v + \sqrt{d(v) + 1}) = O(\sqrt{n_vd(v)} + \sqrt{d_v + 1})$$ where $d(v)$ is the out-degree of $v$, and $n_v$ is the number of neighbours of $v$ with $\ell(v)=\infty$ when $v$ is searched from. Using the Cauchy-Schwarz inequality we can bound the expected running time for all vertices by

@@

and similarly for $\sum_{v \in V} \sqrt{d(v) + 1}$. Hence the claimed running time.

>>>>

In the list model, each vertex is processed in time $$O\big(\sqrt{\frac{n_v}{d(v)}}d_v + \sqrt{d(v) + 1}\big) = O(\sqrt{n_vd(v)} + \sqrt{d_v + 1})$$ where $d(v)$ is the out-degree of $v$, and $n_v$ is the number of neighbours of $v$ with $\ell(v)=\infty$ when $v$ is searched from. Using the Cauchy-Schwarz inequality we can bound the expected running time for all vertices by

@@

and similarly for $\sum_{v \in V} \sqrt{d(v) + 1}$. Hence we have the claimed running time.

### 2018-01-17 CO681-QuantumInformationProcessing/project/quantum-primitives.tex
Wrote up problem 1

Let $T$ be  a table with with $N$ elements, where the $i$-th element is denoted $T[i]$. In a general {\it search problem} we are given $T$ and some $x$ in the universe from which the elements of $T$ are drawn, and are to find some $i \in \{0, \dots, N-1\}$ such that $T[i] = x$. Let $t= |\{ i \in \{0,\dots, N-1\} : T[i] = x\}$. Classically, it is easy to see that when $T$ is unsorted any algorithm which solves this problem with success probability at least $1/2$ will need to make at least $N/2t$ queries to $T$. In contrast, Grover's Quantum Search algorithm will need only $O(\sqrt{N/t})$ queries to have $1/2$ success probability. This is within a constant factor of optimal for a quantum algorithm 

@@

Let $A = \{ i : T[i] = x\}$ and let $B = \{ i : T[i] \neq x \}$. Let $k, \ell \in \R$ satisfying $tk^2 + (N-t)\ell^2 = 1$.  We define the following general quantum register state

@@

Let choose $\theta$ so that $\sin^2\theta = \frac{t}{N}$. Since $t\leq \frac{3}{4}N$, if we let $m_0 = \frac{1}{sin(2\theta)}$ then

@@

recalling (learning?) that the last equality follows from a trigonometric identity. Since $m \geq \frac{1}{\sin(2\theta)}$ after the algorithm passes $c$ iterations, the above probability is at least $\frac{1}{4}$. Therefore the expected number of Grover iterations after the critical stage is

@@

Many of our algorithms in the sections to follow. Particularly in Section \ref{sec:nf} and Section \ref{sec:matching} will use a polynomial number of applications of Grover's search, say $n^d$. If we want all of our quantum subroutines to simultaneously output a correct answer with probability at least $1-\frac{1}{n}$, then we need the probability of failure for a given subroutine to be at most $\frac{1}{n^{d+1}}$. Repeating each subroutine a $\log n$ number of times will ensure this probability. Consequentially, $\log $ factors will appear in our runtimes. We will omit them from the analysis, and cite this note as explanation of their appearance.

@@

Consider the following {\it minima finding } problem, wherein we try to find $d$ smallest values of different types. We are give two functions: an objective $f: \{1, \dots, N\} \rightarrow \N \cup \{\infty\}$, and a type $g: \{1, \dots, N\} \rightarrow \N$. Let $|g| := | \{ g(i): i \in \{1,\dots, N\}\}|$. We are also given an integer $d \in \{, \dots, \min\{|g|, N\}\}$, and are to find $I \subseteq \{1, \dots, N\}$ such that:

@@

Two special case of minima finding are the problems of Finding $d$ Smallest Values of a Function, and Find $d$ Elements of Different Type. By a reduction from distinguishing matrices to these special subproblems, they show in \cite{durr2004quantum} that Minima Finding requires $\Omega(\sqrt{dN})$ queries of $f$ and hence the algorithm we present is optimal. 

>>>>

Let $T$ be  a table with with $N$ elements, where the $i$-th element is denoted $T[i]$. In a general {\it search problem} we are given $T$ and some $x$ in the universe from which the elements of $T$ are drawn, and are to find some $i \in \{0, \dots, N-1\}$ such that $T[i] = x$. Let $$t= |\{ i \in \{0,\dots, N-1\} : T[i] = x\}|.$$ Classically, it is easy to see that when $T$ is unsorted any algorithm which solves this problem with success probability at least $1/2$ will need to make at least $\frac{N}{2t}$ queries to $T$. In contrast, Grover's Quantum Search algorithm will need only $O(\sqrt{N/t})$ queries to have $1/2$ success probability. This is query number is within a constant factor of optimal for a quantum search algorithm 

@@

Let $A = \{ i : T[i] = x\}$ and let $B = \{ i : T[i] \neq x \}$. Let $k, \ell \in \R$ satisfying $$tk^2 + (N-t)\ell^2 = 1.$$ We define the following general quantum register state

@@

Let us choose $\theta$ so that $\sin^2\theta = \frac{t}{N}$. Since $t\leq \frac{3}{4}N$, if we let $m_0 = \frac{1}{sin(2\theta)}$ then

@@

recalling (learning?) that the last equality follows from a trigonometric identity. Since $m \geq \frac{1}{\sin(2\theta)}$ after the algorithm passes $c$ iterations, the above probability is at least $\frac{1}{4}$. Therefore the expected number of Grover iterations after $c$ iterations is

@@

Many of our algorithms in the sections to follow will use a polynomial number of applications of Grover's search, say $n^d$. If we want all of our quantum subroutines to simultaneously output a correct answer with probability at least $1-\frac{1}{n}$, then we need the probability of failure for a given subroutine to be at most $\frac{1}{n^{d+1}}$. Repeating each subroutine a $\log n$ number of times will ensure this probability. Consequentially, $\log $ factors will appear in our runtimes. We will omit them from the analysis, and cite this note as explanation of their appearance.

@@

Consider the following {\it minima finding } problem, wherein we try to find $d$ smallest values of different types. We are give two functions: an objective $f: \{1, \dots, N\} \rightarrow \N \cup \{\infty\}$, and a type $g: \{1, \dots, N\} \rightarrow \N$. Let $|g| := | \{ g(i): i \in \{1,\dots, N\}\}|$. We are also given an integer $d \in \{1, \dots, \min\{|g|, N\}\}$, and are to find $I \subseteq \{1, \dots, N\}$ such that:

@@

Two special cases of minima finding are the problems of Finding $d$ Smallest Values of a Function, and Find $d$ Elements of Different Type. By a reduction from distinguishing matrices to these special subproblems, they show in \cite{durr2004quantum} that Minima Finding requires $\Omega(\sqrt{dN})$ queries of $f$ and hence the algorithm we present is optimal. 

### 2018-01-17 CO749-GraphColoring/assignments/A1.tex
Wrote up problem 1

\documentclass[letterpaper,12pt,oneside,onecolumn]{article}
\usepackage[margin=1in, bottom=1in, top=1in]{geometry} %1 inch margins
\usepackage{amsmath, amssymb, amstext}
\usepackage{fancyhdr}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{theorem}
\usepackage{tikz}
\usepackage{tkz-berge}
\usepackage[braket, qm]{qcircuit}

@@

\lhead{\today}
\rhead{W. Justin Toth CO681-Quantum Information Processing A2} %CHANGE n to ASSIGNMENT NUMBER ijk TO COURSE CODE
\renewcommand{\headrulewidth}{1pt} %heading underlined
%\renewcommand{\baselinestretch}{1.2} % 1.2 line spacing for legibility (optional)

\begin{document}
\section{}
\subsection{a}
\paragraph{}
$$11+12 \mod 13 = 10$$
\subsection{b}
\paragraph{}
$$\Z^\times_{13} = \{2^0=1, 2^1 = 2, 2^2 = 4, 2^3 = 8, 2^4 = 3, 2^5 = 6, 2^6=12, 2^7=11, 2^8 = 9, 2^9=5, 2^{10}=10, 2^{11} = 7\}$$
\subsection{c}
\paragraph{}
$2^8\equiv 9 \mod 13$ so $\log_2(9)$ is $8$ in $\Z^\times_{13}$.
\subsection{d}
\paragraph{}
\begin{itemize}
\item $3^3 \equiv 1 \mod 13$ so $3$ is not a generator
\item $4^6 \equiv 1 \mod 13$ so $4$ is not a generator
\item $5^4 \equiv 1 \mod 13$ so $5$ is not a generator
\item The order of $6$ is $12$ in $\Z_{13}^\times$ so is $6$ is a generator of $Z_{13}^\times$
\item The order of $7$ is $12$ in $\Z_{13}^\times$ so is $7$ is a generator of $Z_{13}^\times$
\item $8^4 \equiv 1 \mod 13$ so $8$ is not a generator
\item $9^3 \equiv 1 \mod 13$ so $9$ is not a generator
\item $10^6 \equiv 1 \mod 13$ so $10$ is not a generator
\item The order of $11$ is $12$ in $\Z_{13}^\times$ so is $11$ is a generator of $Z_{13}^\times$
\item $12 \equiv 1 \mod 13$ so $12$ is not a generator
\end{itemize}
Hence the generators of $\Z_{13}^\times$ besides $2$ are: $6,7,$ and $11$.
\newpage
\section{}
\subsection{a}
\paragraph{}
We check the action of $H$ on $X$ and $Z$.
$$HXH^{\dagger} = \frac{1}{2} \begin{bmatrix} 1 & 1 \\ 1 &  -1 \end{bmatrix} \begin{bmatrix} 0 & 1 \\ 1 & 0 \end{bmatrix} \begin{bmatrix} 1 & 1 \\ 1 &  -1 \end{bmatrix} = \frac{1}{2} \begin{bmatrix} 1 & 1 \\ 1 &  -1 \end{bmatrix} \begin{bmatrix}1 & -1 \\ 1 & 1 \end{bmatrix} =\frac{1}{2} \begin{bmatrix} 2 & 0 \\ 0 & 2 \end{bmatrix} = I. $$
$$HZH^{\dagger} = \frac{1}{2} \begin{bmatrix} 1 & 1 \\ 1 &  -1 \end{bmatrix} \begin{bmatrix} 1 & 0 \\ 0 & -1 \end{bmatrix} \begin{bmatrix} 1 & 1 \\ 1 &  -1 \end{bmatrix} = \frac{1}{2} \begin{bmatrix} 1 & 1 \\ 1 &  -1 \end{bmatrix} \begin{bmatrix} 1 & 1 \\ -1 & 1\end{bmatrix} = \frac{1}{2} \begin{bmatrix} 0 & 2 \\ 2 & 0\end{bmatrix} = X.$$
Thus $H$ is in the Clifford group on $1$ qubit.
\subsection{b}
\paragraph{}
Similar to the previous subsection we consider the action of $T$ on $X$ and $Z$.
$$TXT^{\dagger} = \begin{bmatrix} 1 & 0 \\ 0& \zeta_8 \end{bmatrix}\begin{bmatrix} 0 & 1 \\ 1 & 0 \end{bmatrix}\begin{bmatrix} 1 & 0 \\ 0& \zeta_8^* \end{bmatrix} = \begin{bmatrix} 1 & 0 \\ 0& \zeta_8 \end{bmatrix}\begin{bmatrix} 0 & \zeta^*_8 \\ 1 & 0 \end{bmatrix} = \begin{bmatrix} 0 & \zeta_8^* \\ \zeta_8 & 0 \end{bmatrix}.$$
Such a matrix cannot be written as  $\alpha V$ for phase $\alpha$ and $V \in \{I,X,Y,Z\}$. Thus $T$ is not in Clifford group on $1$ qubit.
\subsection{c}
\paragraph{}
$$SXS^\dagger = \begin{bmatrix} 1 & 0 \\ 0 & i \end{bmatrix} \begin{bmatrix} 0 & 1 \\ 1 & 0 \end{bmatrix} \begin{bmatrix} 1 & 0\\ 0 & -i \end{bmatrix} = \begin{bmatrix} 1 & 0 \\ 0 & i \end{bmatrix} \begin{bmatrix} 0 & -i\\ 1 & 0 \end{bmatrix} =\begin{bmatrix} 0 & -i \\ i & 0 \end{bmatrix} = Y.$$
$$SZS^\dagger = \begin{bmatrix} 1 & 0 \\ 0 & i \end{bmatrix}\begin{bmatrix} 1 & 0 \\ 0 & -1\end{bmatrix} \begin{bmatrix} 1 & 0 \\0 & -i \end{bmatrix} = \begin{bmatrix} 1 & 0 \\ 0 & i \end{bmatrix}\begin{bmatrix} 1 & 0 \\ 0 & i \end{bmatrix} = Z.$$
Thus $S$ is in the Clifford group on $1$ qubit.
\subsection{d}
\paragraph{}
Let $C$ be the unitary matrix representing the controlled-not gate. We consider the action of $C$ on $I \otimes X$, $X\otimes I$, $I \otimes Z$. and $Z \otimes I$.
$$C (I\otimes X) C^\dagger = \begin{bmatrix} 1 & 0 & 0 & 0 \\ 0 & 1 & 0 & 0 \\ 0 & 0 & 0 &1 \\ 0& 0& 1 & 0 \end{bmatrix}\begin{bmatrix}0 & 1 & 0 & 0 \\ 1 & 0 & 0 &0 \\ 0 & 0 &0 & 1 \\ 0 & 0 & 1 & 0 \end{bmatrix} \begin{bmatrix} 1 & 0 & 0 & 0 \\ 0 & 1 & 0 & 0 \\ 0 & 0 & 0 &1 \\ 0& 0& 1 & 0 \end{bmatrix} = \begin{bmatrix} 0 & 1& 0& 0\\ 1 & 0  & 0& 0\\ 0 & 0 & 1 & 0\\ 0 & 0 & 0 & 1\end{bmatrix} \begin{bmatrix} 1 & 0 & 0 & 0 \\ 0 & 1 & 0 & 0 \\ 0 & 0 & 0 &1 \\ 0& 0& 1 & 0 \end{bmatrix} = I \otimes X.$$
$$ C (X \otimes I) C^\dagger =  \begin{bmatrix} 1 & 0 & 0 & 0 \\ 0 & 1 & 0 & 0 \\ 0 & 0 & 0 &1 \\ 0& 0& 1 & 0 \end{bmatrix} \begin{bmatrix}  0 & 0 & 1 & 0 \\ 0 & 0 & 0 & 1 \\ 1 & 0 & 0 & 0 \\ 0 &1 & 0 &0\end{bmatrix} \begin{bmatrix} 1 & 0 & 0 & 0 \\ 0 & 1 & 0 & 0 \\ 0 & 0 & 0 &1 \\ 0& 0& 1 & 0 \end{bmatrix}  =  \begin{bmatrix} 0 & 0 &1 & 0 \\ 0 & 0 & 0 & 1 \\ 0 & 1 & 0 & 0 \\ 1 & 0 & 0 &0\end{bmatrix} \begin{bmatrix} 1 & 0 & 0 & 0 \\ 0 & 1 & 0 & 0 \\ 0 & 0 & 0 &1 \\ 0& 0& 1 & 0 \end{bmatrix} = X \otimes X$$
\begin{align*}C (I \otimes Z) C^\dagger &=  \begin{bmatrix} 1 & 0 & 0 & 0 \\ 0 & 1 & 0 & 0 \\ 0 & 0 & 0 &1 \\ 0& 0& 1 & 0 \end{bmatrix}\begin{bmatrix}1 &0 &0 &0 \\ 0 & -1 & 0 &0 \\ 0 & 0 &1 & 0\\ 0& 0& 0 & -1 \end{bmatrix} \begin{bmatrix} 1 & 0 & 0 & 0 \\ 0 & 1 & 0 & 0 \\ 0 & 0 & 0 &1 \\ 0& 0& 1 & 0 \end{bmatrix}\\
 &=  \begin{bmatrix} 1 & 0 & 0 &0 \\ 0 & -1 & 0 &0 \\ 0 & 0 & 0 & -1 \\ 0 &0 &1 & 0\end{bmatrix}\begin{bmatrix} 1 & 0 & 0 & 0 \\ 0 & 1 & 0 & 0 \\ 0 & 0 & 0 &1 \\ 0& 0& 1 & 0 \end{bmatrix}\\ &= \begin{bmatrix} 1 & 0 &0 &0 \\ 0 & -1 &0 &0 \\ 0 &0 &-1 & 0\\ 0 &0 &0 &1\end{bmatrix} = Z \otimes Z.\end{align*}
 \begin{align*}
 C(Z\otimes I)C^\dagger &=  \begin{bmatrix} 1 & 0 & 0 & 0 \\ 0 & 1 & 0 & 0 \\ 0 & 0 & 0 &1 \\ 0& 0& 1 & 0 \end{bmatrix} \begin{bmatrix}1 &0 &0 &0 \\0 & 1 & 0 &0 \\ 0 &0 &-1 & 0\\ 0 &0 &0 & -1 \end{bmatrix}  \begin{bmatrix} 1 & 0 & 0 & 0 \\ 0 & 1 & 0 & 0 \\ 0 & 0 & 0 &1 \\ 0& 0& 1 & 0 \end{bmatrix}\\
 &= \begin{bmatrix} 1& 0 & 0 &0 \\0 &1 & 0 &0 \\ 0 & 0 &0 &-1 \\ 0 & 0 & -1 &0\end{bmatrix} \begin{bmatrix} 1 & 0 & 0 & 0 \\ 0 & 1 & 0 & 0 \\ 0 & 0 & 0 &1 \\ 0& 0& 1 & 0 \end{bmatrix}\\
 &= \begin{bmatrix} 1 & 0 &0 &0 \\ 0 &1 & 0 &0\\ 0 & 0 &-1 & 0 \\ 0 & 0 & 0 & -1 \end{bmatrix} = Z\otimes I.
 \end{align*}
 Thus $C$ is in the $2$-qubit Clifford group.
 \subsection{e}
 Let $A$ be the Toffoli gate (CCNOT). For the sake of space we'll abbreviate the calculations. We have that
 $$A(I\otimes X\otimes I) A^\dagger = \begin{bmatrix} X\otimes I & 0 \\ 0 & Z\otimes Z\end{bmatrix}.$$
 This can't be written as a tensor product $\alpha V_1\otimes V_2 \otimes V_3$ with $\alpha$ scalar and $V_1,V_2, V_3 \in \{I,X,Y,Z\}$. To see this observe that if we take $V_1 \in  \{X, Y\}$ then the first $4x4$ diagonal block of $V_1\otimes V_2 \otimes V_3$ will be $0$, contradicting that it should be $X \otimes I$, and if we take $V_1 \in \{I,Z\}$ then the first $4x4$ diagonal block will be $\pm1$ times the second, but $X\otimes I \neq \pm Z\otimes Z$. Therefore no such tensor product expression for $A(I\otimes X \otimes I)A^\dagger$ is possible, and hence the Toffoli gate is not in the $3$-qubit Clifford group. $\blacksquare$
 \newpage\section{}
 \subsection{a}
 \paragraph{}
We use the same notation for gates as in question $2$. $X_4$ is given by the circuit
 \[ \Qcircuit @C=1em @R=1em {
 & \targ &   \qw & \qw\\
 & \ctrl{-1} & \gate{X} & \qw
}\]
$Z_4$ is given by the circuit
\[ \Qcircuit @C=1em @R=1em {
 & \gate{S} &  \gate{S} & \qw\\
 & \gate{S} & \qw & \qw
}\].
\subsection{b}
\paragraph{}
$X_8$ is given by the circuit (using one Toffoli gate)
\[ \Qcircuit @C=1em @R=1em {
 & \targ &  \qw & \qw & \qw & \qw\\
 & \ctrl{-1} & \targ& \qw  & \qw &\qw\\
 & \ctrl{-1} & \ctrl{-1} & \gate{X} &\qw & \qw
}\]
Bonus: Figure $4.9$ of Nielsen and Chuang gives a controlled single-qubit implementation of the Toffoli gate. Since my use of the Toffoli gate has different controls I reflect the picture, giving the following implementation of the above Toffoli gate where the first qubit is controlled by the second and third:

\[ \Qcircuit @C=1em @R=1em {
 & \gate{H} & \targ & \gate{T^\dagger} & \targ & \gate{T} & \targ & \gate{T^\dagger}& \targ & \gate{T} & \gate{H} & \qw & \qw & \qw \\
 & \qw & \ctrl{-1}& \qw  & \qw & \qw & \ctrl{-1} & \qw & \qw & \gate{T^\dagger} & \targ & \gate{T^\dagger} & \targ & \gate{S} &\qw\\
 & \qw & \qw & \qw & \ctrl{-2} & \qw & \qw & \qw & \ctrl{-2} & \qw & \ctrl{-1} & \qw & \ctrl{-1} & \gate{T} & \qw
}\]
$Z_8$ is given by the circuit
\[ \Qcircuit @C=1em @R=1em {
 & \gate{T} &  \gate{T} & \gate{T} & \gate{T} & \qw\\
 & \gate{T} & \gate{T}& \qw  & \qw &\qw\\
 & \gate{T} & \qw & \qw &\qw & \qw
}\]
\newpage
\section{}
\subsection{a}
\paragraph{}
We can express $F_d, F_d^{-1}, X_d$, and $Z_d$ as sums or rank one matrices as follows:
$$F_d = \frac{1}{\sqrt{d}} \sum_{j,k \in \Z_d} \omega^{j k} \ket{j}\bra{k}$$
$$F_d^{-1} = \frac{1}{\sqrt{d}} \sum_{j,k \in \Z_d} \omega^{- j k} \ket{k}\bra{j}$$
$$X_d = \sum_{k \in \Z_d} \ket{k+1 \mod d} \bra{k}$$
$$Z_d = \sum_{k \in \Z_d} \omega^k \ket{k}\bra{k}$$
where $\omega := \exp(2\pi i / d)$.
\paragraph{}
Then we have
\begin{align*}
F_dX_dF_d^{-1} &= \frac{1}{d} \sum_{j,k \in \Z_d} \omega^{j k} \ket{j}\bra{k}\sum_{k \in \Z_d} \ket{k+1 \mod d} \bra{k}\sum_{j,k \in \Z_d} \omega^{- j k} \ket{k}\bra{j}\\
&= \frac{1}{d} \sum_{j,k \in \Z_d} \omega^{j k} \ket{j}\bra{k} \sum_{j,k \in \Z_d} \omega^{- j k} \ket{k+1 \mod d}\bra{j} \\
&= \frac{1}{d} \sum_{j,k,\ell \in \Z_d}\omega^{\ell(k+1\mod d)}\omega^{-jk}\ket{\ell}\bra{j} \\
&=\frac{1}{d} \sum_{j,k,\ell \in \Z_d}\omega^{\ell(k+1)}\omega^{-jk}\ket{\ell}\bra{j}  \quad\text{(we may drop mod since $\omega^{\ell 0 } = \omega^{\ell d} = 1$)} \\
&= \frac{1}{d} \sum_{j,k,\ell \in \Z_d}\omega^{k(\ell-j)}\omega^{\ell}\ket{\ell}\bra{j} \\
&= \sum_{\ell \in \Z_d} \omega^\ell \ket{\ell}\bra{\ell} \quad \text{(applying Kronecker Delta summing over $k$)} \\
&= Z_d.
\end{align*}
So $F_d X_d F_d^{-1} = Z_d$. Thus we have (we will show the desired form of $F_d^2$ is part $b$)
\begin{align*}
F_dZ_d F_d^{-1} &= F_d^2 X_d F_d^{-2} \\
&= \sum_{k \in Z_d} \ket{-k \mod d} \bra{k} \sum_{k \in \Z_d} \ket{k+1 \mod d}\bra{k} \sum_{k \in \Z_d} \ket{k}\bra{-k\mod d} \\
&= \sum_{k \in Z_d} \ket{-k \mod d} \bra{k} \sum_{k \in Z_d}\ket{k+1 \mod d}\bra{-k \mod d} \\
&= \sum_{k \in Z_d} \ket{-(k+1) \mod d} \bra{- k \mod d} \\
&= \sum_{k \in Z_d} \ket{k+1 \mod d} \bra{k \mod d} \\
&= X_d.
\end{align*}
Hence $F_d Z_d F_d^{-1} = X_d$.
\subsection{b}
Let $p \in \Z_d$. Then we have
\begin{align*}
F^2_d\ket{k} &= \frac{1}{d} \sum_{j,k \in \Z_d} \omega^{j k} \ket{j}\bra{k}\sum_{j,k \in \Z_d} \omega^{j k} \ket{j}\bra{k} \ket{p} \\
&= \frac{1}{d} \sum_{j,k \in \Z_d} \omega^{j k} \ket{j}\bra{k}\sum_{j \in \Z_d}\omega^{jp}\ket{j} \\
&=\frac{1}{d} \sum_{j,k \in \Z_d} \omega^{k(j+ p)}\ket{j}.
\end{align*}
For fixed $j$, $$\frac{1}{d} \sum_{k \in \Z_d} \omega^{k(j+p)} = 1$$ if and only if $$j+p = 0 \mod d$$ and otherwise $$\frac{1}{d} \sum_{k \in \Z_d} \omega^{k(j+p)} = 0$$. Hence 
$$F^2_d \ket{k} = \ket{-k \mod d}$$
and so
$$F^2_d = \sum_{k \in \Z_d} \ket{-k \mod d} \bra{k}.$$
\subsection{c}
Since $-0 \mod d \equiv 0$ and $-d/2 \mod d \equiv d/2$ ($d$ is even), we have that
$$F^2_d \ket{0} = \ket{0}$$
and $$F^2_d\ket{d/2} = \ket{d/2}$$
so $1$ is an eigenvalue of $F^2_d$. Further, let $k \in \Z_d \backslash \{0, d/2\}$. Then
$$F^2_d(\ket{k} + \ket{-k \mod d}) = (\ket{k} + \ket{-k \mod d})$$
and
$$F^2_d(\ket{k} - \ket{-k \mod d}) = -\ket{k} + \ket{-k\mod d}$$
so $-1$ is another eigenvalue of of $F^2_d$, and we have found a basis of $\C^d$ consisting of eigenvectors of $F_d^2$ (the two eigenvectors generated for each such $k$ above, and $\ket{0}$ and $\ket{d/2}$). Hence we have found all eigenvalues of $F^2_d$. That is the eigenvalues of $F^2_d$ are precisely $\pm 1$.
\subsection{d}
\paragraph{}
We check the action of $F_4$:
\begin{align*}
F_4(X\otimes I) F_4^{-1} &= \frac{1}{4} \sum_{j,k = 0}^3 \omega^{jk}\ket{j}\bra{k}(\ket{2}\bra{0} + \ket{3}\bra{1} + \ket{0}\bra{2} + \ket{1}\bra{3})\sum_{j,k = 0}^3 \omega^{-jk}\ket{k}\bra{j}\\
&= \frac{1}{4} \sum_{j,k = 0}^3 \omega^{jk}\ket{j}\bra{k}(\sum_{\ell=0}^3 \ket{\ell}\bra{\ell + 2 \mod 4})\sum_{j,k=0}^3\omega^{-jk}\ket{k}\bra{j}\\
&=  \frac{1}{4} \sum_{j,k = 0}^3 \omega^{jk}\ket{j}\bra{k}\sum_{\ell,j=0}^3 \omega^{-j(\ell+2)}\ket{\ell}\bra{j} \\
&=\frac{1}{4} \sum_{j,k,\ell=0}^3 \omega^{jk}\omega^{-\ell(k+2)}\ket{j}\bra{\ell} \\
&=\frac{1}{4} \sum_{j,k,\ell=0}^3\omega^{-2\ell} \omega^{k(j-\ell)} \ket{j}\bra{\ell}\\
&=\sum_{\ell=0}^3\omega^{-2\ell} \ket{\ell}\bra{\ell}\\
&= I \otimes Z.
\end{align*}
\begin{align*}
F_4(I\otimes X) F_4^{-1} &= \frac{1}{4} \sum_{j,k = 0}^3 \omega^{jk}\ket{j}\bra{k}(\ket{1}\bra{0} + \ket{0}\bra{1} + \ket{3}\bra{2} +\ket{2}\bra{3})\sum_{j,k = 0}^3 \omega^{-jk}\ket{k}\bra{j} \\
&= \frac{1}{4}(\sum_{j,k=0}^3(\omega^{j} + \omega^{-k} + \omega^{3j - 2k} + \omega^{2j - 3k}))\ket{j}\bra{k} \\
&= \ket{0}\bra{0} + -i\ket{3}\bra{1} - \ket{2}\bra{2} + i \ket{1}\bra{3}
\end{align*}
which cannot be written as a tensor product of $\{I, X, Y, Z\}$. Hence $F_4$ is not in the Clifford group.
\newpage\section{}
\paragraph{}
Suppose that $m$ is prime. Let $\lambda \in \Z_m$. Let $r \in \Z_m\times \Z_m \backslash \{(0,0)\}$. We may assume without loss of generality that $r_1 \neq 0$. We define $L_\lambda$ and $\ket{L_\lambda}$ as in the question preamble. Then we have
\begin{align*}
(F^{-1}_m \otimes F^{-1}_m) \ket{L_\lambda} &= \frac{1}{\sqrt{m}} \sum_{j,k \in \Z_m} \frac{1}{m} \sum_{(x_1,x_2) \in L_\lambda}\omega^{x_1j + x_2k}\ket{j}\ket{k}.
\end{align*}
For a fixed $j,k \in \Z_m\times \Z_m$ the $\ket{j}\ket{k}$ term in the above vanishes iff $\sum_{(x_1,x_2) \in L_\lambda}\omega^{x_1j + x_2k} = 0$.  From the hint we know that $$\sum_{s \in \Z_m} \omega^s = 0.$$
Hence the $\ket{j}\ket{k}$ term vanishes iff for all $s \in \Z_m$ there exists $(x_1,x_2) \in L_\lambda$ such that $x_1j + x_2k = s$ (this establishes a bijection from $L_\lambda$ to $\Z_m$, proving $\abs{L_\lambda} = m$, as we'll see below such $x$ must be unique).
\paragraph{}
For all $s \in \Z_m$ we want $x \in \Z_m \times \Z_m$ satisfying
$$x_1j + x_2k = s \quad\text{and}\quad x_1r_1 + x_2r_2 = \lambda.$$
This system has no solution provided
$$jr_1 = kr_2 \quad \text{and} \quad s -kr_1^{-1}\lambda\neq 0 \quad(\text{mod } m)$$
The first condition is satisfied iff $(j,k)$ is a scalar multiple of $(r_1,r_2)$. Given that the first condition is satisfied, the second condition is satisfied for all $s \in \Z_m$, save $s = -r^{-1}_1k\lambda$. Thus we have
$$(F^{-1}_m \otimes F^{-1}_m) \ket{L_\lambda} = \frac{1}{\sqrt{m}} \sum_{\alpha \in \Z_m} \omega^{\alpha \lambda}\ket{\alpha r_1}\ket{\alpha r_2}.$$
So measuring this state will yield a scalar multiple of $(r_1,r_2)$ each with equal probability. This does not reveal any information about $\lambda$.
\end{document}

>>>>

\documentclass[letterpaper,12pt,oneside,onecolumn]{article}
\usepackage[margin=1in, bottom=1in, top=1in]{geometry} %1 inch margins
\usepackage{amsmath, amssymb, amstext}
\usepackage{fancyhdr}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{theorem}
\usepackage{tikz}
\usepackage{tkz-berge}
\usepackage[braket, qm]{qcircuit}
\usepackage{hyperref}

@@

\lhead{CO 749 - \today}
\rhead{W. Justin Toth - A1} %CHANGE n to ASSIGNMENT NUMBER ijk TO COURSE CODE
\renewcommand{\headrulewidth}{1pt} %heading underlined
%\renewcommand{\baselinestretch}{1.2} % 1.2 line spacing for legibility (optional)

\begin{document}
\section{}
\paragraph{}
Let $G$ be a graph of minimum degree at least $3$ satisfying all of the following:
\begin{itemize}
	\item Every triangle contains at most one vertex of degree three.
	\item If two vertices of degree three are adjacent then they are in triangles.
	\item No two distinct triangles share a common edge.
\end{itemize}
Suppose for a contradiction that $\abs{E(G)} < 5\abs{V(G)}/3$.
\begin{claim}\label{1.1}
	For every $v \in V(G)$, if $d(v) = 3$ then $v$ has at most one neighbour of degree $3$.
\end{claim}
\begin{proof}
	Assume for a contradiction that there exist $u,v, w \in V(G)$ satisfying
	$$d(u) = d(v) = d(w) = 3$$
	and $uv, vw \in E(G)$, i.e. $u$ and $w$ are adjacent to $v$. But then, using the second property of $G$, $v$ is in a triangle. Denote this triangle by $C$. Since every triangle contains at most one vertex of degree three, $u$ and $w$ are not contained in $C$. But then since $d(v) = 3$, $v$ has at most one neighbour in $C$, a contradiction to $C$ being a $K_3$.
\end{proof}
\paragraph{}
We proceed by a discharging argument. For each vertex $v \in V(G)$ set the initial charge as
$$ch_0(v) = d(v) - 4$$
and for each edge $e \in E(G)$ set the initial charge
$$ch_0(e) = 1/3.$$
Then our total charge is, using handshaking,
\begin{align*}
\sum_{v\in V(G)} ch_0(v) + \sum_{e \in E(G)} ch_0(e) &= \sum_{v \in V(G)} d(v) - 4|V(G)| + \frac{1}{3} |E(G)|\\ &=  \frac{7}{3}|E(G)| - 4|V(G)\\ &< \frac{35}{9}|V(G)| - \frac{36}{9}|V(G)|\\ &< 0
\end{align*}
with the first inequality following from our assumption that $|E(G)| < 5|V(G)|/3$.
\paragraph{}
Redistribute the charge, to obtain $ch_1$, according to the following Rules:
\begin{enumerate}
	\item If edge $uv$ contains precisely one vertex $u$ such that $d(u) = 3$ then $uv$ sends $1/3$ charge to $u$.
	\item If edge $uv$ is such that $d(u) \geq 4$ and $d(v) \geq 4$ and $u,v$ are in a triangle with vertex $w$ then $uv$ sends $1/3$ charge to $w$.
\end{enumerate}
\paragraph{}
Since vertices sends no charge, clearly every vertex $v \in V(G)$ with $d(v) \geq 4$ has $$ch_1(v) = ch_0(v) \geq 0.$$ Now we will show that if $v$ is a vertex with $d(v) = 3$ then $ch_1(v) \geq 0$. From Claim \ref{1.1} $v$ is adjacent with at most one vertex of degree $3$. If $v$ is adjacent with no degree three vertices then each edge incident with $v$ sends $\frac{1}{3}$ charge to $v$ by Rule $1$ and hence
$$ch_1(v) = ch_0(v) + 3\cdot\frac{1}{3} = 0.$$
On the other hand, if $v$ is adjacent with one degree three vertex then $v$ receives $\frac{2}{3}$ charge from incident edges by Rule $1$. The remaining needed $\frac{1}{3}$ is obtained from Rule $2$ as follows. Since $v$ is adjacent with a degree three vertices, $v$ lies in a triangle, and since every triangle contains at most one degree three vertex the edge containing the other two vertices of this triangle sends $\frac{1}{3}$ charge to $v$. Therefore $ch_1(v) \geq 0$.
\paragraph{}
It remains to verify that each edge $uv$ satisfies $ch_1(uv) \geq 0$. Edge $uv$ can satisfy at most one of Rule $1$ and Rule $2$. If $uv$ satisfies Rule $1$ it sends $\frac{1}{3}$ charge and so $ch_1(uv) = 0$. Instead if $uv$ satisfies Rule $2$ it can only do so for one triangle, since no two distinct triangles share a common edge. So $uv$ only sends $\frac{1}{3}$ charge by Rule $2$. Therefore $ch_1(uv) \geq 0$.
\paragraph{}
Therefore we have a contradiction as our total charge is negative but $ch_1$ of each object is non-negative.$\blacksquare$
\end{document}
